---
title: "Data Download"
---

```{r, warning=FALSE, message=FALSE}
library(rvest)
library(magrittr)
library(stringr)
library(stringi)
library(tidyverse)
```

#Create the drugs look-up - 'drugs_list'
```{r}
#Get a list of links to test
drugs_list <- readLines("https://bnf.nice.org.uk/interaction/") %>%
  str_match_all("<a href=\"(.*?)\"><span>(.*?)</span>") %>%
  unlist() %>%
  data.frame()

#Replace odd characters
drugs_list$. <- str_replace(drugs_list$., "&#233;", replacement = "é")

#Create a dataframe from it.
drugs_list <-  drugs_list %>%
  data.frame(cbind(observation = rep(1:(nrow(drugs_list)/3), each=3))) %>%
  data.frame(cbind(class = c("String", "Link", "Title"))) %>%
  rename(value = '.') %>%
  spread(key=class, value=value)

#Remove non-drug links
drugs_list <- drugs_list %>%
  filter(stri_detect_fixed(drugs_list$Link, "title=") == FALSE)

#Remove defunct columns
drugs_list <- drugs_list %>%
    select(-observation) %>%
    select(-String)

#Remove some leftover tags
drugs_list$Title <- str_replace(drugs_list$Title, "<sub>", replacement = "")
drugs_list$Title <- str_replace(drugs_list$Title, "</sub>", replacement = "")

#Add a string column
drugs_list <- cbind(drugs_list, 
                    string = str_replace(drugs_list$Link, ".html", replacement = ""))

#Add CSS tag and URL columns
drugs_list <- cbind(drugs_list, 
                    url = str_c("https://bnf.nice.org.uk/interaction/", 
                                drugs_list$string, ".html"))
drugs_list <- cbind(drugs_list, css_string = str_c("#", drugs_list$string, " .interactant span"))

#Convert to character classes
drugs_list[] <- lapply(drugs_list, as.character)

#Set a timestamp for the data collection
drugs_listDatestamp <- Sys.Date()
```

#Compare to the last 'drugs_list'
This requires an original drugs_list for the first attempt.
To get around this you could take a drugs_list from a fork/clone of this repository.
Or you could save the drugs list you've just created.
i.e.

example <- drugs_list
then run "kept <- .." onwards

```{r, message=FALSE, warning=FALSE}
example <- read_csv("archive/drugs_list.csv")

kept <- intersect(drugs_list$Link, example$Link)
newdrugs <- setdiff(drugs_list$Link, example$Link)
removed <- setdiff(example$Link, drugs_list$Link)

rm(example)
```

You also need an 'archive' folder in the cd, as well as a 'data'.
Otherwise you'll get an error message when you run write_csv.

#Export the 'drugs_list' differences
```{r}
#create folder for archive date
dir.create(str_c("archive/", drugs_listDatestamp))

#if there are new drugs, save in a date-labelled folder newdrugs.csv
if (length(newdrugs) > 0) {
  label <- str_c("archive/", drugs_listDatestamp, "/") %>%
  str_c("newdrugs.csv")
write_csv(data_frame(newdrugs), path = label)
#could save .Rda too
}
#if there are removed drugs, save in a date-labelled folder removeddrugs.csv
if (length(removed) > 0) {
  label <- str_c("archive/", drugs_listDatestamp, "/") %>%
  str_c("removeddrugs.csv")
write_csv(data_frame(removed), label)
#could save .Rda too
}

#export drugs_list
label <- str_c("archive/", drugs_listDatestamp, "/") %>%
  str_c("drugs_list.csv")
write_csv(drugs_list, label)

label <- str_c("archive/", drugs_listDatestamp, "/") %>%
  str_c("drugs_list.Rda")
save(drugs_list, file=label)

#Overwrite as the most recent drugs_list 
write_csv(drugs_list, "archive/drugs_list.csv")
#could keep one in /data as well, but I only use it here, so I don't see why bother
rm(label)
```

#Scrape the data
```{r}
data <- sapply(drugs_list$url, function(x)
               read_html(x) %>%
               list())

#Set a timestamp for the data collection
Timestamp <- Sys.time()
Datestamp <- Sys.Date()

#could export data here if I needed
```

#Construct an interactions database from 'data'
```{r}
##Title
dataframe <- data.frame(Title = drugs_list$Title)

##Interactions
alli <- lapply(data,
                function(url){
                    url %>% 
                    html_nodes(css = ".interactant span") %>%
                    html_text()
                })

#Set ordinal factor for severity
severity <- c("NotSet", "Unknown", "Mild", "Moderate", "Severe")
severity <- factor(severity, levels=c("NotSet", "Unknown", "Mild", "Moderate", "Severe"), ordered=TRUE)

#All Severity
severityi <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")
lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]]) > 1) {
  sections[[x1]] %>% 
    html_children() %>% 
    html_attr("class") %>% 
    str_replace_all("interaction-message  ", "") %>% 
    max()
  } else {
  sections[[x1]] %>% 
     html_children() %>% 
     html_attr("class") %>%
     str_replace_all("interaction-message  ", "")
  }
  }
) %>%
unlist()
})

#All Evidence
evidencei <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")

lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]] %>% 
    html_nodes("dd~ dd")) > 0) {
  sections[[x1]] %>% 
    html_nodes("dd~ dd") %>%
    html_text() %>%
    min()
  } else {
  as.character("NotSet")
  }
  }
) %>%
unlist()
})

#Combine multiple divs under one interaction
infoi <- lapply(1:length(data), function(x) {
sections <- html_nodes(data[[x]], "div.span9.interaction-messages")

lapply(1:length(sections), function(x1, x){
#Returns Max value in multiples.
if (length(sections[[x1]]) > 1) {
  sections[[x1]] %>% 
    html_nodes(css = ".interaction-message div") %>% 
    html_text() %>% 
    str_replace_all("\n", replacement="") %>% 
    str_trim() %>% 
    paste(sep="", collapse="")
  } else {
  sections[[x1]] %>% 
    html_nodes(css = ".interaction-message div") %>% 
    html_text() %>% 
    str_replace_all("\n", replacement="") %>% 
    str_trim()
  }
  }
) %>%
unlist()
})

#Bind columns
dataframe <- cbind(dataframe, 
                           data_frame(alli), 
                           data_frame(severityi),
                           data_frame(evidencei),
                           data_frame(infoi))

#Rename columns
dataframe <-  dataframe %>%
  rename(Interactions = 'alli',
         Severity = 'severityi', 
         Evidence = 'evidencei',
         'Interactions Info' = 'infoi')

##Totals
dataframe$'Interaction Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(alli[[x]]))
                })
dataframe$'Severity Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$Severity[[x]]))
                })
dataframe$'Evidence Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$Evidence[[x]]))
                })
dataframe$'Interactions Info Total' <- lapply(1:nrow(dataframe), function(x){
                    unlist(length(dataframe$'Interactions Info'[[x]]))
                })
#not sure yet if I still require the totals - used later in data completion
rm(alli)
rm(severityi)
rm(evidencei)
rm(infoi)
```

#Check data completion
```{r}
dataframe$'Complete Data' <- lapply(1:nrow(dataframe), function(x){
                    if (dataframe$`Interaction Total`[[x]] == dataframe$`Severity Total`[[x]] &
                        dataframe$`Interaction Total`[[x]] == dataframe$`Interactions Info Total`[[x]]  &
                        dataframe$`Interaction Total`[[x]] == dataframe$`Evidence Total`[[x]])
                    {TRUE} else {FALSE}
})
```

Everything there?
```{r}
sum(unlist(dataframe$'Complete Data')) == nrow(dataframe)
```

Export dataframe
```{r, eval=FALSE}
#going to save under drugs_listDatestamp folder, in-case slightly older than Datestamp
#Datestamp == drugs_listDatestamp
dataframeName <- str_c("archive/", drugs_listDatestamp, "/") %>%
  str_c("dataframe.Rda")

#label <- str_c("archive/", drugs_listDatestamp, "/") %>%
#  str_c("dataframe.csv")
#write_csv(dataframe, label)
#doesn't quite like the lists.

save(dataframe, file=dataframeName)
rm(label, dataframeName)
```

Make a databse for JSON Format
```{r}
#Create a new database
master <- dataframe %>%
  select('Title', 'Interactions', 'Severity', 'Evidence', 'Interactions Info') %>%
  rename(name = 'Title',
         imports = 'Interactions')
master$title <- master$name

#Added an unlabled column
master$importstitle <- master$imports

#master
master$name <- as.character(master$name)
master$name <- trimws(master$name, "both")

master$title <- as.character(master$title)
master$title <- trimws(master$title, "both")

##remove odd characters in $name
faultycharacters <- str_detect(master$name, "\\(") | str_detect(master$name, string="\\)") | grepl(pattern = "/", x = master$name) | grepl(pattern = "'", x = master$name) | grepl(pattern = ",", x = master$name)
faultyvalues <- master$name[faultycharacters]
faultyvaluesindex <- which(faultycharacters)

##remove odd characters in $name
for (i in faultyvaluesindex){
 master$name[i] <- master$name[i] %>%
  stri_replace_all_regex(pattern = "/", replacement = " ") %>%
  str_replace_all(pattern = "\\(", replacement = "") %>%
  str_replace_all(pattern = "\\)", replacement = "") %>%
  stri_replace_all_regex(pattern = "'", replacement = "") %>%
  stri_replace_all_regex(pattern = ",", replacement = "")
}

for (i in 1:length(master$imports)){
example <- list()
example[[1]] <- master$imports[i] %>%
  unlist() %>%
  stri_replace_all_regex(pattern = "/", replacement = " ") %>%
  str_replace_all(pattern = "\\(", replacement = "") %>%
  str_replace_all(pattern = "\\)", replacement = "") %>%
  stri_replace_all_regex(pattern = "'", replacement = "") %>%
  stri_replace_all_regex(pattern = ",", replacement = "")
master$imports[i] <- example
}

#Relabel 'name'
master$name <- str_c("BNF.", master$name, ".", master$name) %>%
  str_replace_all(pattern=" ", replacement="")

#Relabel 'interactions'
node.parent.child <- function(x) {
  example <- master[x,] %>%
    select('imports') %>%
    unlist() %>%
    as.character() 
  
  example <- str_c(".", example) %>%
    str_dup(times=2)
  
  example <- str_c("BNF", example) %>%
    str_replace_all(pattern=" ", replacement="")
  return(as.vector(example))
}
master$imports <- lapply(1:nrow(master), node.parent.child)

#add timestamp
master$Stamp <- Timestamp

##Need to add new? true/false column
#master$new <- drugs_list$url
index <- match(newdrugs, drugs_list$Link)
master$new <- 1:nrow(master) %in% index

##bnflink url column
master$bnflink <- drugs_list$url

rm(index, i)
```

#Save in /archive, and /data
```{r}
#latest one in the archive, overwrites previous
master %>%
  jsonlite::toJSON() %>%
  write(file="archive/master.json")

#latest one, date-labelled in archive
jsonName <- str_c("archive/", drugs_listDatestamp, "/master.json")
master %>%
  jsonlite::toJSON() %>%
  write(file = jsonName)

label <- str_c("archive/", drugs_listDatestamp, "/master.Rda")
save(master, file=label)

#latest one in data, overwrites previous
master %>%
  jsonlite::toJSON() %>%
  write(file="data/master.json")

rm(jsonName, label)
```

#Create Top 100
Shortlist in R, or rewrite javascript to use full data?